Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-12 paper.tex
I forgot to remove and rename this. :D

The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes, and shows a set of definitions of the regression methods applied in the paper as well as the evaluation metrics considered.
Then, Section \ref{sec:problem} introduces the problem of the estimation of print run
% (Paloma) Guys, 'print run' is written a total of 28 times:
% 23 are in the 'print-run' form
% 5 are 'print-run' (with a dash), of which one is inside the list of variables. But what about the rest inside text? Shouldn't they go ALL either with or without the dash?
% Antonio - I have replaced all of them by 'print run' as it seems to be the correct one
for new books, along with a description of the considered dataset.
Section \ref{sec:methodology} details the methodology considered in the study. These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies. Obtained results for the four considered special cases are commented in Section \ref{sec:example_cases}. Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.

%********************************************************************************
\section{Background and State of the art on sales forecasting} 
\label{sec:soa}

>>>>

The rest of this paper is structured as follows: next, Section \ref{sec:soa} presents a comprehensive review of the approaches found in the bibliography related to sales prediction in similar scopes.
Then, Section \ref{sec:problem} introduces the problem of the estimation of print run
% (Paloma) Guys, 'print run' is written a total of 28 times:
% 23 are in the 'print-run' form
% 5 are 'print-run' (with a dash), of which one is inside the list of variables. But what about the rest inside text? Shouldn't they go ALL either with or without the dash?
% Antonio - I have replaced all of them by 'print run' as it seems to be the correct one
for new books, along with a description of the considered dataset.
Section \ref{sec:methodology} details the methodology considered in the study. These are reported in Section \ref{sec:experiments}, which is also devoted to analyse the obtained results in feature selection and book sales forecasting using different datasets, with different amounts of features, for all the publishing companies. Obtained results for the four considered special cases are commented in Section \ref{sec:example_cases}. Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusionsAndFutureWork}.

%********************************************************************************
\section{State of the art on sales forecasting} 
\label{sec:soa}
